West Africa cuckoo stopover rainfall patterns

### 2018-04-25 stopover_rainfall_vis.Rmd
Changes from laptop work 3rd week of Apr

library(ggplot2)

@@

int_out$country<-factor(int_out$country, levels= c("Angola", "Democratic Republic of the Congo",
                                                   "Congo", "Gabon", "Central African Republic", 
                                                   "Cameroon", "Nigeria", "Togo", "Burkina Faso",
                                                   "Ghana", "Cote d'Ivoire", "Liberia", "Guinea", 
                                                   "Sierra Leone"))
outlist<-list()
for( i in 2012:2017)
  {
  int1<-int_out[int_out$year==i,]

@@

szr<-length(unique(paste(int_out[int_out$ptt==j & int_out$year==i,]$country,int_out[int_out$ptt==j & int_out$year==i,]$SO_startDOY )))

temp=ggplot(data=int_out[int_out$ptt==j & int_out$year==i,], 
          aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=50), fill='grey')+
  geom_bar(stat='identity', colour='black')+
  geom_smooth(span=0.5, se=FALSE, linetype='dashed', col='red')+
  facet_wrap(~SO_startDOY+country)+theme_classic()+
  ylab('daily rainfall (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding, "   Mig speed:", round(dtemp$m4c_resid, 2)))

outlist[[paste(szr, i, j)]]<-temp
print(temp)

>>>>

library(ggplot2)
library(dplyr)

@@

int_out$country<-factor(int_out$country, levels= c("Angola", "Democratic Republic of the Congo",
                                                   "Congo", "Gabon", "Central African Republic", 
                                                   "Cameroon", "Nigeria", "Togo", "Burkina Faso",
                                                   "Ghana", "Cote d'Ivoire", "Liberia", "Guinea", 
                                                   "Sierra Leone"))
int_out[is.na(int_out$value),]$value<-0
int_out$ID2<-paste(int_out$SO_startDOY, int_out$country)

for( i in 2012:2017)
  {
  int1<-int_out[int_out$year==i,]

@@

t1<-int_out[int_out$ptt==j & int_out$year==i,]

t2<-t1 %>% group_by(ID2) %>% dplyr::mutate(cumrf=cumsum(value))

temp=ggplot(data=t2,aes(x=variable, y=value))+
geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=500), fill='grey')+
  geom_bar(stat='identity', colour='black')+
    geom_line(aes(y=cumrf), col='green', size=1)+
  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
  ylab('cumulative rainfall since 01 Jan (mm)')+ xlab('Day of year')+
          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", dtemp$arrive_breeding, "   Mig speed:", round(dtemp$m4c_resid, 2)))

print(temp)

#temp=ggplot(data=t2,aes(x=variable, y=value))+
#geom_rect(aes(xmin=SO_startDOY, xmax=SO_endDOY, ymin=0, ymax=50), #fill='grey')+
#  geom_bar(stat='identity', colour='black')+
#  geom_smooth(span=0.5, se=FALSE, linetype='dashed', col='red')+
#  facet_wrap(~country+SO_startDOY, scales='free_y')+theme_classic()+
#  ylab('daily rainfall (mm)')+ xlab('Day of year')+
#          ggtitle(paste("Year:",i,"   PTT:", j, "   Arr date:", #dtemp$arrive_breeding, "   Mig speed:", round(dtemp$m4c_resid, 2)))
